A data-intensive assessment of the species-abundance distribution.

### 2015-04-02 defense_pres.tex
Expands methods section.

\section{The species abundance distribution}
\subsection{Pattern description}
\begin{frame}[t]{}
\frametitle{Commonness \& rarity}
~\\
\begin{large}
The species abundance distribution:
\end{large}
\begin{itemize}
\item Describes the distribution of commonness \& rarity of species.
\item One of the most fundamental and ubiquitous patterns in ecology.
\item Exhibits a hollow curve distribution.
\begin{itemize}
\item Many rare species.
\item Few common species.
~\\
\end{itemize}
\item Many forms of the species abundance distribution (SAD).
\end{itemize}
\end{frame}

\subsection{Forms of the distribution}
\begin{frame}
\frametitle{Forms of the SAD}
Statistical description\\  
\includegraphics[scale=.2]{./sad-data/dissertation/Preston1948.png}\\

@@

\subsubsection{Analysis}
\begin{frame}
\frametitle{SAD Comparisons}
~\\
Analysis:
\begin{itemize}
\item Model fitting with maximum likelihood estimation. 
\item Likelihood based model selection to compare the fits of the different models.
\item Model comparison with corrected Aikaike Information Criterion (AICc) weights.
\end{itemize}
\end{frame}

@@

@@

>>>>

\section{The species abundance distribution}
\subsection{Pattern description}
\begin{frame}[t]{}
\frametitle{Commonness \& rarity}
~\\
\begin{large}
The species abundance distribution:
\end{large}
\begin{center}
\includegraphics[scale=.52]{./sad-data/dissertation/genericRAD.png}\\
\end{center}
\note{
\begin{itemize}
\item Describes the distribution of commonness \& rarity of species.
\item One of the most fundamental and ubiquitous patterns in ecology.
\item Exhibits a hollow curve distribution.
\begin{itemize}
\item Many rare species.
\item Few common species.
~\\
\end{itemize}
\end{itemize}}
Many models of the species abundance distribution (SAD).
\end{frame}

\subsection{Forms of the distribution}
\begin{frame}[t]
\frametitle{SAD models}
Statistical description\\  
\includegraphics[scale=.2]{./sad-data/dissertation/Preston1948.png}\\

@@

\subsubsection{Analysis}
\begin{frame}[t]
\frametitle{SAD Comparisons}
~\\
Analysis:
\begin{itemize}
\item Model fitting with maximum likelihood estimation.\\
~\\
$l_x(\theta) = \log h(x) + \log f_\theta(x)$
\end{itemize}
\end{frame}

\begin{frame}[t]
\frametitle{SAD Comparisons}
~\\
Analysis:
\begin{itemize}
\item Likelihood based model selection to compare the fits of the different models.
\begin{itemize}
\item Assess the fit of the model without corrections for parameter number or similarity to other models.
\item How well does the model describe the data?
\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[t]
\frametitle{SAD Comparisons}
~\\
Analysis:
\begin{itemize}
\item Model comparison with corrected Aikaike Information Criterion (AICc) weights.
\begin{itemize}
\item Assess the fit of the model correcting for parameter number and small sample size.
\item How well does the model describe the data relative to the number of parameters?
\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}{}
\frametitle{SAD Comparisons}
\includegraphics[scale=.5]{./sad-data/chapter1/Zipf_weights.png}
\end{frame}

@@

\begin{frame}{}
\frametitle{SAD Comparisons}
\includegraphics[scale= 1]{./sad-data/dissertation/Zipf_one_to_one.png}
\end{frame}
